Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-02 lloveras_2020.tex
nuevos graficos

\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$). It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results. Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results. As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height. To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results. For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines. This is a LOT of information from which and we need to pull out a few clear conlcusions.}

The thermodynamic results of AWSoM are shown in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}. That is latitude-longitude maps for $\Ne$ and $\Te$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the same open-close boundary showed in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} respectively.

%$r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.

A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions. The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$. In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.

>>>>

\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$). It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results. Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results. As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height. To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results. For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines. This is a LOT of information from which and we need to pull out a few clear conclusions.}

Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature, for both rotations. These Figures show the results at the same three heights selected for visualisation of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}. As in those, thick-black curves indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model. Visual inspection of these maps shows that the AWSoM model for both rotations is highly axysimmetric, as the tomographic model.

\diego{A visual inspection of these maps shows that both reconstructions are very axysimmetric for $\Ne$ and $\Te$ as well. The closed region is denser and hotter than the open region. The density and temperature gradients are maximum in the open-close boundary. The open field regions in low latitudes maintain thermodynamic values associated with open regions.} The reconstruction of CR-2082 does not show clear the ARs, while CR-2208 shows a well reconstruction of both AR around latitude-longitud $+5\mdeg$, $140\mdeg$ and $+5\mdeg$, $300\mdeg$. In both rotations the open-closed boundaries derived from the AWSoM model match the shape of the contour levels of both the electron density and the electron temperature.
